Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
fixed broken todo

\paragraph{Comparing two data sets:} We used the social data\todo{Confusing,
  since you proceed to say you build a dataset with technical factors as well as
  social factors.} gathered to create two data 
sets: one with only the technical
factors and the build status, and another with both the technical and social
factors. We performed this split to analyze how well technical factors alone,
and then both technical and social
factors predict build integration status.

@@

\todo{Maybe ``relationship with'' rather than ``effect on''?

>>>>

\paragraph{Comparing two data sets:} We compiled all the gather data into 
two data sets: one with only the technical
factors and the build status, and another with both the technical and social
factors and the build status. We performed this split to analyze how well technical factors alone,
and then both technical and social
factors predict build integration status.

@@

\todo{Maybe ``relationship with'' rather than ``effect on''?}
